---
title: "HW1"
author: 'Brooke Grazda'
format: html
editor: visual
---
# Data Modeling & Database Management

## Appendix
CREATE TABLE Species (
    Code TEXT PRIMARY KEY,
    Common_name TEXT UNIQUE NOT NULL,
    Scientific_name TEXT,
    Relevance TEXT
);

CREATE TABLE Site (
    Code TEXT PRIMARY KEY,
    Site_name TEXT UNIQUE NOT NULL,
    Location TEXT NOT NULL,
    Latitude REAL NOT NULL CHECK (Latitude BETWEEN -90 AND 90),
    Longitude REAL NOT NULL CHECK (Longitude BETWEEN -180 AND 180),
    "Total_Study_Plot_Area_(ha)" REAL NOT NULL
        CHECK ("Total_Study_Plot_Area_(ha)" > 0),
    UNIQUE (Latitude, Longitude)
);

CREATE TABLE Snow_survey (

  Snow_cover INTEGER
  Water_cover INTEGER
  Land_cover INTEGER
  Total_cover INTEGER
)

CREATE TABLE Color_band_code (
    Code TEXT PRIMARY KEY,
    Color TEXT NOT NULL UNIQUE
);

CREATE TABLE Personnel (
    Abbreviation TEXT PRIMARY KEY,
    Name TEXT NOT NULL UNIQUE
);
```{r, warning=FALSE}
#| message: false
#| code-fold: true
# Import libraries
library(tidyverse)
library(here)
```
### Data Exploration
```{r}
snow_survey <- read_csv(here('ASDN_csv', 'ASDN_Snow_survey.csv'))

glimpse(snow_survey)

# The number of unique values at location must be true for all number of rows in the column
length(unique(snow_survey$Location)) == length(snow_survey$Location) # Returns False

# Must return True to be a primary key


```

```{r}
na_count <-sapply(snow_survey, function(y) sum(length(which(is.na(y)))))
na_count <- data.frame(na_count)

kableExtra::kable(na_count)
```

## Reference Example
CREATE TABLE Species (
    Code TEXT PRIMARY KEY,
    Common_name TEXT UNIQUE NOT NULL,
    Scientific_name TEXT,
    Relevance TEXT
);

CREATE TABLE Site (
    Code TEXT PRIMARY KEY,
    Site_name TEXT UNIQUE NOT NULL,
    Location TEXT NOT NULL,
    Latitude REAL NOT NULL CHECK (Latitude BETWEEN -90 AND 90),
    Longitude REAL NOT NULL CHECK (Longitude BETWEEN -180 AND 180),
    "Total_Study_Plot_Area_(ha)" REAL NOT NULL
        CHECK ("Total_Study_Plot_Area_(ha)" > 0),
    UNIQUE (Latitude, Longitude)
);

CREATE TABLE Color_band_code (
    Code TEXT PRIMARY KEY,
    Color TEXT NOT NULL UNIQUE
);

CREATE TABLE Personnel (
    Abbreviation TEXT PRIMARY KEY,
    Name TEXT NOT NULL UNIQUE
);


```{sql}
CREATE TABLE Place (
  Site TEXT PRIMARY KEY,
  Plot TEXT, 
  Location TEXT 
);

CREATE TABLE Survey (
  ID INTEGER PRIMARY KEY,
  Year DOUBLE NOT NULL,
  Date DATE NOT NULL (Between 2006-06-04 AND 2014-08-05),
  Snow_cover DOUBLE NOT NULL,
  Water_cover DOUBLE NOT NULL,
  Land_cover DOUBLE NOT NULL,
  Total_cover DOUBLE NOT NULL,
  Notes TEXT ,
  FOREIGN KEY (Obs_ID) REFERENCES Surveyor(ID),
  FOREIGN KEY (Site) REFERENCES Place(Site),
);

CREATE TABLE Surveyor (
  ID INTEGER PRIMARY KEY,
  Observer TEXT NOT NULL
);
```












